---
title: "exponential distribution"
author: "Thierry Musy"
date: "08.18.2015"
output: pdf_document
---

Investigation on the exponential distribution
----------------------------------------
In this PDF the exponential distribution is investigated.

## Simulation setup

## Mean
The theoretical mean of a exponential distribution is 1/lambda. With lambda set to 0.2 the mean is:

mean = 1 / lambda = 1/0.2 = lambda^-1 = 5

```{r}
lambda = 0.2
theoretical_mean = lambda^-1
```

The sample mean is caculated by running 1000 time the mean of 40 exponential distribution.

```{r}
mns = NULL
for (i in 1: 1000) mns = c(mns, mean(rexp(40, 0.2)))
hist(mns)
x <- seq(0, 10, length=100)
hx <- dnorm(x, mean=5)
lines(x, hx*500, col="green", lwd=2)
abline(v=5, col="red", lwd=2)
```

As we can see in the histogram the mean concentrades around the expected theoretical mean of 5.

## Variance
The theoretical variance of a exponential distribution is lambda^-2. With lambda set to 0.2 the variance is:

variance = lambda^-2 = 25

```{r}
theoretical_variance = lambda^-2
```

The sample variance is caculated by running 1000 time the variance of 40 exponential distribution.

```{r}
vars = NULL
for (i in 1: 1000) vars = c(vars, var(rexp(40, 0.2)))
hist(vars)
abline(v=25, col="red", lwd=2)
```

As we can see in the histogram the variance concentrades around the expected theoretical variance of 25.
