---
title: "exponential distribution"
author: "Thierry Musy"
date: "18. August 2015"
output: pdf_document
---

Investigation on the exponential distribution
----------------------------------------
In this PDF the exponential distribution is investigated.

## Simulation setup

## Mean
The theoretical mean of a exponential distribution is 1/lambda. With lambda set to 0.2 the mean is:

mean = 1 / lamda = 1/0.2 = lamda^-1 = 5

```{r}
theoretical_mean = lambda^-1
```

The sample mean is caculated by running 1000 time the mean of 40 exponential distribution.

```{r}
mns = NULL
for (i in 1: 1000) mns = c(mns, mean(rexp(40, 0.2)))
hist(mns)
```

## Variance
The theoretical variance of a exponential distribution is lambda^-2. With lambda set to 0.2 the variance is:

mean = lamda^-2 = 25

```{r}
theoretical_variance = lambda^-2
```

The sample variance is caculated by running 1000 time the variance of 40 exponential distribution.

```{r}
mns = NULL
for (i in 1: 1000) mns = c(mns, mean(rexp(40, 0.2)))
hist(mns)
```


You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
